### 2013-09-17 chi2014/introduction.tex
Minor edits to intro

In this paper, we focus on crowd-based brainstorming. While brainstorming has been an implicit component of many creative endeavors in microtask marketplaces, we are unaware of any research that specifically describes and models brainstorming in this environment. Furthermore, while there is a rich literature describing brainstorming processes of individuals and groups (e.g., \cite{osborn_applied_1957, pinsonneault_electronic_1999, nijstad_how_2006} OTHERS?), microtask marketplaces are qualitatively different from previously studied environments, calling into question how much of this past research maps onto this environment. For example, brainstorming participants in a microtask marketplace are paid for their participation, and are often eager to complete a task as fast as possible to move on to the next paying task [REF?]. Given these and other differences, there are many open questions about how brainstorming unfolds in this context.

>>>>

In this paper, we focus on crowd-based brainstorming. While brainstorming has been an implicit component of many creative endeavors in microtask marketplaces, we are unaware of any research that specifically describes and models the brainstorming process in this environment. Furthermore, while there is a rich literature describing brainstorming processes of individuals and groups (e.g., \cite{osborn_applied_1957, pinsonneault_electronic_1999, nijstad_how_2006} OTHERS?), microtask marketplaces are qualitatively different from previously studied environments, calling into question how much of this past research maps onto this environment. For example, brainstorming participants in a microtask marketplace are paid for their participation, and are often eager to complete a task as fast as possible to move on to the next paying task [REF?]. Given these and other differences, there are many open questions about how brainstorming unfolds in this context.
